### 2015-06-26 scyllarus-and-mifd.tex
Reference to ontology of attacks

{\ids} fusion proper begins with
\textbf{Clustering.} From the
sensor reports, MIFD generates \emph{event hypotheses} to represent the
underlying events of interest that may have caused the sensor reports.  A
sensor report that provides evidence for an event hypothesis is a
\emph{supporter}.
The clustering process constructs a
directed graph of event hypothesis and sensor report nodes forming a
Bayesian belief network.

>>>>

{\ids} fusion proper begins with
\textbf{Clustering.} From the
sensor reports,
and based on an ontology detailing how (and with what probability)
sensor reports may correspond to events,
MIFD generates \emph{event hypotheses} to represent the
underlying events of interest that may have caused the sensor reports.  A
sensor report that provides evidence for an event hypothesis is a
\emph{supporter}.
The clustering process constructs a
directed graph of event hypothesis and sensor report nodes forming a
Bayesian belief network.
